---
title: "BI612 H4"
author: "Natasha Hannan"
output: html_document
---

```{r}
library(readr)
titanic <- read_csv("~/BI612-homework/titanic.csv")
```

#2 
1- Gender - females will likely have a greater chance of survival
2- Age - a younger person will have a greater chance of survival due to the fact that they would be first priority 
3- Class - People in a lower class will likely survive more then higher classes
4- Parch (parents/children on board) - people will more family members on board are likely to survive compared to those without
5- Fare - people that paid more for their ticket liekly have more money and therefore are more likely to survive. 


#3 
```{r}
library(vcd)
mosaic(survived~Gender, data=titanic)
library(vcd)
mosaic(survived~pclass, data=titanic)
library(popbio)
titanic.nona<-na.omit(data.frame("age"=titanic$age,"survived"=titanic$survived))
logi.hist.plot(titanic.nona$age,titanic.nona$survived,boxp=FALSE,type="hist",col="gray", xlabel="Age")
library(popbio)
titanic.nona<-na.omit(data.frame("fare"=titanic$fare,"survived"=titanic$survived))
logi.hist.plot(titanic.nona$fare,titanic.nona$survived,boxp=FALSE,type="hist",col="gray", xlabel="Fare")
library(popbio)
titanic.nona<-na.omit(data.frame("parch"=titanic$parch,"survived"=titanic$survived))
logi.hist.plot(titanic.nona$parch,titanic.nona$survived,boxp=FALSE,type="hist",col="gray", xlabel="Number of parents/children on board")
```

#4 
```{r}
library(bestglm)
my.variables=data.frame("gender"=titanic$Gender,"class"=titanic$pclass,"age"=titanic$age,"fare"=titanic$fare,"parch"=titanic$parch,"survived"=titanic$survived)
my.variables.nona=na.omit(my.variables)
bestglm(my.variables.nona,IC="AIC",family=binomial)
```

#5
```{r}
model1<-glm(survived~gender+class+age, data=my.variables.nona)
summary.lm(model1)
```
#6
```{r}
univariate.gender=glm(survived~gender, data=my.variables.nona, family=binomial(link="logit"))
summary(univariate.gender)
univariate.age=glm(survived~age, data=my.variables.nona, family=binomial(link="logit"))
summary(univariate.age)
univariate.class=glm(survived~class, data=my.variables.nona, family=binomial(link="logit"))
summary(univariate.class)
univariate.fare=glm(survived~fare, data=my.variables.nona, family=binomial(link="logit"))
summary(univariate.fare)
univariate.parch=glm(survived~parch, data=my.variables.nona, family=binomial(link="logit"))
summary(univariate.parch)
```

```{r}
model2<-glm(survived~gender+age+class+parch, data=my.variables.nona, family=binomial(link="logit"))
summary(model2)
```


```{r}
model3<-glm(survived~gender+age+class, data=my.variables.nona, family=binomial(link="logit"))
summary(model3)
```
```{r}
library(lmtest)
lrtest(model1,model3)
```

#7 Purposeful selection did create a model that was better then automatic. The loglikelihood is more negative which indicated that it is better.

#8
```{r}
library(effects)
plot(allEffects(model1))
```
Yes, all of the effects were in the expected direction. Females, people in a lower class and younger people had a greater change of survival.

#9
```{r}
library(car)
residualPlots(model1)
outlierTest(model1)
influenceIndexPlot(model1,id.n=3)
influencePlot(model1)
vif(model1)
print(model1)
```

#10 In the regression diagnostics there were some values that were seen as outliers and hadf a greater affect, those values include data line 29, 94, 264 and 1109.

#11
```{r}
library(caret)
ctrl <- trainControl(method = "repeatedcv", number = 10, savePredictions = TRUE)
my.variables.nona$survived=as.factor(my.variables.nona$survived)
train(survived~gender+age+class,data=my.variables.nona, method="glm", family=binomial(link='logit'),trControl = ctrl, tuneLength = 5)
```

#12 Based on the k-fold results, the model did a good job of predicting survival at around 78% accuracy.


#13
```{r}
predictions<-predict(model1, newdata=my.variables.nona,type="response")
confusionMatrix(data=as.factor(as.numeric(predictions>0.5)),reference=my.variables.nona$survived)
```
The accuracy of the model was about 78%.

#14 I think that there is a difference in accuracy between the k-fold and confussion matrix because they are calculated differently. 
